\large COOPERATIVE 3-D MAP GENERATION USING MULTIPLE UAVS

### 2015-05-15 draft.tex
Significant updates to thesis.

% Abstract
\begin{abstract}
  In the modern field of robotics, the ability for a robot to smoothly move about the environment, regardless of the medium, has proven to be fairly trivial. However, the ability for a mobile robot to track its own position and make deterministic decisions about it's own location in a foreign environment remains a fundamental, but critical problem. In most typical robotic experiments, the use of external measurement systems (such as GPS or motion capture cameras) allow researchers to capture the exact position of a robot in its environment and focus on other areas of interest. In the past couple decades, successful algorithms called SLAM\footnote{Simultaneous-Localization-And-Mapping: algorithm that uses sensor data to independently determine a position relational to an environment and simultaneously create a virtual map} have allowed singular mobile robots to determine their own position in a world space and construct a 3-D map from collected positional data. However, despite these advances, the ability for multiple UAV\footnote{UAV: unmanned aerial vehicle} robots to cooperatively determine their environmental boundaries is an area that remains relatively under-developed. Some studies have attempted this decentralized, cooperative approach, but fall short either by depending on external systems or lacking true 3-D capability. By taking this distributional approach with multiple robotic agents, the computational overhead of map generation is greatly reduced. Teams of coordinated robots could efficiently explore unaccessible areas, complete team-based tasks (like lifting large objects), conduct dangerous search and rescue missions, and ultimately increase the feasibility of robotics in numerous situations.
\end{abstract}
\clearpage

@@

\section{Overview}
\section{Literature Review}

In recent research projects with quadcopters, a wide variety of methods have been used to localize a robot in their environment, including (but not limited to) the use of high-resolution laser scanners \cite{bachrach2011range,shen2011autonomous}, monocular cameras \cite{soundararaj2009autonomous}, and ``RGB-D"\footnote{RGB-D: red-blue-green-depth} cameras as a combination of the two \cite{huang2011visual}. A laser has been used to generate a point cloud and pull out contours that trace the environment\cite{bachrach2011range}, a monocular camera to exploit texture gradients and continuations that can translated into depth estimates \cite{soundararaj2009autonomous}, and Microsoft Kinects (RGB-D cameras) to associate laser depth with image data \cite{huang2011visual}. Lasers capable of such precision and frequency are economically infeasible, and additionally, a pure visual approach is slow, can result in large margins of error, and lacks precision. Using a combination of the two, by means of an RGB-D camera, is responsive,  inexpensive, and produces results of reasonable reliability.

@@

Researchers have also attempted de-centralized SLAM methods like I have proposed, but do not provide total three-dimensional capability. Some have used a VICON camera system \cite{leung2012decentralized} to provide true location data to robotic agents. Others have implemented truly autonomous, cooperative SLAM, but only focused on 2-D, planar data analysis \cite{cunningham2012large}. As I have mentioned previously, this does not fully address the ability to move and coordinate multiples robot entities independently in a realistic world setting. By examining this precedent work in the field, however, the ability to create cooperative 3-D SLAM can be fully visualized.

@@

Several key design decisions arose when choosing a direction for robot design and selection of components. The most signifcant choice for the robot was choosing an architecture for the onboard computational unit - specifically an ARM or x86 computer. The second key design dilemma involved the selection of a laser-scanning sensor or an RGB-D camera. As shown below, both these choices had great effect upon the path of experimentation and results obtained.

@@

The main advantage of choosing an x86 board (found in most desktop or laptop computers) is compatibility. Almost all software packages are available in prebuilt, binary form on package managers (such as Ubuntu's apt-get) and setting up the computing environment can be done with a few simple installation commands. This convenience, unfortunately, comes at a financial and dimensional price - most small form-factor x86 boards are extremely expensive and cheaper options are considerably larger in size. These tradeoffs make selection of such a board unfeasible for an aerial drone where space is extremely limited and minimization of cost is a primary concern. As a result, ARM boards (like those in smartphones) are much more attractive - they offer extremely small form-factors, yet remain very affordable. The issue that arises, of course, is that of compatibility - many programs or libraries are not (immediately) available on an ARM installation and require manual compilation of source code using an ARM-based compiler and possible changes to the source code itself first.

@@

The two major choices of sensors for robotic vision are using a laser scanner or an RGB-D camera. Much like the x86 computers, lasers are a terrific choice when cost is not a concern - they have wide field of view (some providing between 270 and 360 degrees), can scan very quickly (40 scans per second), and have amidable range (around 30 meters). However, a single unit can cost upwards of five thousand dollars. An RGB-D camera, like the Microsoft Kinect, are very cheap sensor in comparison (the Kinect only costing only \$99 per unit). Unlike the laser, these sensors provide both depth and camera image data. However, they are slower (maximum of 30 scans per second) and require sigificantly more bandwidth for data transmission.

@@

The hardware design of the robot was focused on using low-cost, off-the-shelf components (see Table 1). The approximate cost of a built robot was \$894, significantly cheaper than pre-built alternatives such as the AscTec Pelican used at MIT \cite{bachrach2011range} and University of Washington \cite{bachrach2012estimation} with similar project requirements.

% Table of components used on robot
\begin{table}[h!]
  \centering
  \caption{Table of Components}
  \vspace{2mm}
  \begin{tabular}{l l l}
    \hline \hline
    \vspace{-2mm}
    Component & \multicolumn{1}{l}{Description} & \multicolumn{1}{l}{Cost} \\ [1ex]
    \hline
    & \\
    DJI F450 Frame & Chassis & \$200 \\
    DJI 1045 Propellers & Props & \$10 \\
    DJI 2212 Motors & Actuators & \$30 \\
    12V and 5V Regulators & Power Reg. & \$40 \\
    Zippy 2450 mAh LiPo & Battery & \$30 \\
    64GB ODROID XU3 & ARM SBU & \$240 \\
    Pixhawk PX4 & Controller & \$220 \\
    Microsoft Kinect & Visual Sensor & \$99 \\
    MaxSonar EZ0	& Sonar Sensor & \$25 \\
  \end{tabular}
\end{table}

\noindent The robot used a stock F450 frame from DJI, which was not modified in any way - all components were mounted on existing areas using screws or adhesive products.

@@

\noindent The onboard computational unit chosen was the ODROID XU3 by HardKernel, which has a 1.7Ghz quad-core Snapdragon CPU, 2GB DDR3 RAM, 64GB eMMC flash storage, USB 3.0, and draws 5A. Initially, the robot was equipped with a PandaBoard ES, possessing a 1.2Ghz dual core with 1GB DDR3 RAM, SD card storage, and drawing 3A. Due to low memory and high read/write latencies, the latter board struggled to bear the load of even a full Ubuntu installation and was replaced with the XU3. For the visual sensor, a stripped down Microsoft Kinect Model 1473 was mounted onto the quadcopter - removing the sensor housing reduced weight from a heavy 3 lb to a very nimble 100 g. A Pixhawk PX4 flight controller was also added to the system for actuation control - this allowed the focus of the project to remain on the mapping and flight components of the robot. To accomodate the 12V, 1A requirements of the Kinect and 5V, 5A of the ODROID, several power regulators were mounted and installed to the robot's power system. The entire system was powered by a single 2450 mAh LiPo battery.

@@

@@

Robot Operating System (ROS) is a \"meta\" operating system that is installed as package on a UNIX-based OS like Ubuntu or OS X. In a nutshell, ROS allows one to design their robot in a distributed model, where each ROS \"node\" is essentially a process or computational component of the robot. It also provides asynchronous and synchronous communication libraries, network libraries, and supports multiple programming languages. Usage of ROS in the project allowed focus to remain on algorithm development and away from grunt work.

% ROS architecture
\begin{figure}[h!]
 \caption{Photograph of finished quadcopter robot.}
 \centering
   \includegraphics[width=0.4\textwidth]{images/ros_arch}
\end{figure}

As shown in figure X, the robot was split into several nodes.

\subsection{RGBDSLAM\_V2}
\noindent In order to compute a 3D map, the quadcopter's onboard computer uses an algorithm called SLAM (simultaneous localization and mapping) which computes a map and keeps track of the robotic agent's pose and translation relative to said map. Due to time constraints, it was decided that a proprietary SLAM algorithm was not an option and a previously developed software package was chosen instead. Due to it's compatibility with ROS and extensive accpetance throughout the robotics community, RGBDSLAM_V2 was the software used to produce the map and pose transformations of the robot during flight.

% RGBDSLAM data flow
\begin{figure}[h]
 \caption{Data flow of RGBDSLAM_V2}
 \centering
   \includegraphics[width=0.6\textwidth]{images/rgbdslam}
\end{figure}

@@

The direction of my project has two major stages to complete: Designing the robot and developing the navigation and map-building algorithms. \\

@@

@@

Coupled with the mapping component of the RGBDSLAM package, a custom ROS node was written (integrated with RGBDSLAM) that provided a stream of clouds added to the map to through a new ROS topic, each corresponding to new nodes added within the graph. As shown in \ref{fig: online stream.}, these clouds and their respective transforms\footnote{The transform of the cloud is that between the RGB optical frame of the Kinect camera and the fixed frame of the robot's map.} are computed by RGBDSLAM, sent procedurally over the network, received by a server or other external computer, which then executes the online map builder algorithm for each cloud. The algorithm first matches the new cloud $\bf{P_n}$ with its transform $\bf{T_n}$ by performing a transformation lookup keyed by the timestamp $\bf{t_n}$ of the cloud (located in its header data). Once located, the transformation is applied to the cloud, changing its pose to be relative to the aggregate map $\bf{P_a}$. Once this transformation is applied, the new cloud can be simply appended to the current aggregate cloud in the simple operation $\bf{P_a} += \bf{P_n}$  - this new version of the cloud $\bf{P_a}$ is then saved into a database or filesystem.

@@

    \noindent Within the alignment process itself, there are several subprocesses. First, the normals $N_{source}$ and $N_{target}$ are found by PCL's normal estimator. These normal clouds are then used in PCL's Fast Point Feature Histogram (FPFH) \cite{rusu2009fast,rusu2009fastlabel} estimator, to generate approximate feature clouds $F_{source}$ and $F_{target}$. These feature clouds store feature descriptors for each point in the cloud, in this case, FPFH features. Although, the theory behind image features is beyond the scope of this report, the FPFH feature approximates the mean curvature of a point's k-neighbors' geometry with a histogram of values - this type of feature allows computation of a feature cloud in asympototically linear time, giving a powerful but relatively quick feature estimator. Lastly, these feature clouds from this process are used to estimate an initial transformation $T$, which is applied to the initial source cloud to obtain an initial alignment. This gives the clouds a reasonably close placement relative to each other, and allowing optimal usage of ICP in order to fine tune them.

@@

    \noindent After the clouds have passed through the initial alignment stage, they are locally optimized using the Iterative Closest Point algorithm. ICP takes a point cloud $P_{source}$ and finds the nearest neighbor points in $P_{target}$. By minimizing the sum of squares error, a rigid transformation $T$ between $P_{source}$ and $P_{target}$ is output. As shown in Figure ~\ref{fig:SCIA alignment.}, this transformation is applied to $P_{source}$ which eliminates narrower errors between the two clouds.

@@

    Lastly, the target and transformed source cloud are concatenated using Point Cloud Library's concatentation features - programmatically, this is as simple as just adding the clouds together. Using another Voxel filter, the excess data points are trimmed away to generate the final stitched version of the map, as shown in Figure ~\ref{fig:ICP alignment.}. \\

@@

@@

% Table of Map Fusion parameters
\begin{table}[h!]
  \centering
  \caption{Map Fusion Parameters}
  \vspace{2mm}
  \begin{tabular}{l l}
    \hline \hline
    \vspace{-2mm}
    Parameter & \multicolumn{1}{l}{Value} \\ [1ex]
    \hline
    & \\
    Voxel Leaf Size & 0.05 \\
    ICP Max. Corresp. Dist. & 0.1 \\
    ICP Max. Iter. & 50 \\
    ICP Trans. Epsilon & 1e-8 \\
    ICP Euclid. Epsilon & 1 \\
    SCIA Min. Sample. Dist & 1 \\
    SCIA Max. Corresp. Dist & 1 \\
    SCIA Max. Iter. & 50 \\
  \end{tabular}
\end{table}

>>>>

% Abstract
\begin{abstract}

\noindent This report aims to demonstrate the feasibility of building a global 3-D map from multiple UAV robots in a GPS-denied, indoor environment. Presented are the design of each robot and the reasoning behind choosing its hardware and software components, the process in which a single robot obtains a individual 3-D map independently of external communication, and lastly how the mapping concept is extended to multiple robotic agents to form a global 3-D map using a centralized server. In the latter section, this report focuses on two algorithms, \textsl{Online Mapping} and \textsl{Map Fusion}, developed to facilitate the cooperative approach. A limited selection of experiments and test results are also presented to demonstate application of these algorithms in a real-world setting.

\end{abstract}
\clearpage

@@

In the modern field of robotics, the ability for a robot to move about the environment, regardless of the medium, has proven to be fairly trivial. However, the ability for a robot to track its own position and make deterministic decisions about it's own location in a foreign environment remains a fundamental, but critical problem. In most typical robotic experiments, the use of external measurement systems (such as GPS or motion capture cameras) allows researchers to capture the exact position of a robot in its environment and focus on other areas of interest. In the past couple decades, successful algorithms called SLAM\footnote{Simultaneous-Localization-And-Mapping: algorithm that uses sensor data to independently determine a position relational to an environment and simultaneously create a virtual map} have allowed singular robots to determine their own position in a world frame and construct a 3-D map from collected positional data. However, despite these advances, the ability for multiple UAV\footnote{UAV: unmanned aerial vehicle} robots to cooperatively determine their environmental boundaries is an area that remains relatively under-developed. By taking this cooperative approach with multiple robots, teams of coordinated robots could efficiently explore unaccessible areas, complete team-based tasks (like lifting large objects), conduct dangerous search and rescue missions, etc. This report explores the feasibility of mapping an indoor environemnt using multiple UAV robots where external positioning systems are not available. It should be noted that the navigation component of a robot using a SLAM system was not the focus of this project - the experiments and algorithms within instead concentrate on the computational and communicative aspects of developing a global map in such an environment.

\section{Literature Review}

In recent research projects with quadcopters, a wide variety of methods have been used to localize a robot in their environment, including (but not limited to) the use of high-resolution laser scanners \cite{bachrach2011range,shen2011autonomous}, monocular cameras \cite{soundararaj2009autonomous}, and ``RGB-D"\footnote{RGB-D: red-blue-green-depth} cameras as a combination of the two \cite{huang2011visual}. A laser has been used to generate a point cloud and pull out contours that trace the environment\cite{bachrach2011range}, a monocular camera to exploit texture gradients and continuations that can translated into depth estimates \cite{soundararaj2009autonomous}, and Microsoft Kinects (RGB-D cameras) to associate laser depth with image data \cite{huang2011visual}. Lasers capable of such precision and frequency are economically infeasible, and additionally, a pure laser approach is slow, can result in large margins of error, and lacks precision. Using a combination of the two, by means of an RGB-D camera, is responsive,  inexpensive, and produces results of reasonable reliability.

@@

In recent years, researchers have attempted cooperative mapping methods similar to what's discussed in this report. Walter et al. showed experiments using cooperative SLAM in underwater vehicles \cite{walter2004experimental}. Riazuelo et al. developed the $C^{2}TAM$ cloud framework for cooperative tracking and mapping using UAVs \cite{riazuelo2014c}, where mapping and optimization is computed in the cloud. A few researchers have even demonstrated de-centralized SLAM methods, but either do not provide total three-dimensional capability or use external positioning sensors. For instance, Leung et al. used a VICON camera system \cite{leung2012decentralized} to provide true location data to decentralized robotic agents. Cunningham et al. implemented truly autonomous decentralized SLAM, but only focused on 2-D, planar data analysis \cite{cunningham2012large}.

This project attempts to build on this precedent by demonstrating cooperative mapping with UAVs as opposed to ground or aquatic robots. In addition, the mapping process is computed completely onboard the robot (as opposed to the cloud) and a centralized server is only used with the introduction of the cooperative component. Lastly, the robots used in this report are capable of building and communicating a completely three dimensional map as opposed to 2.5D or completely two dimensional data.

@@

Several key design decisions arose when choosing a direction for robot design and selection of components. The most signifcant choice for the robot was choosing an architecture for the onboard computational unit - specifically an ARM or x86 computer. The second key design dilemma (as mentioned briefly in the literature review) involved the selection of a laser-scanning sensor or an RGB-D camera. As shown below, both these choices had great effect upon the path of experimentation and results obtained.

@@

The main advantage of choosing an x86 board (found in most desktop or laptop computers) is compatibility. Almost all software packages are available in prebuilt, binary form on package managers (such as Ubuntu's apt-get) and setting up the computing environment can be done with a few simple installation commands. This convenience, unfortunately, comes at a financial and dimensional price - most small form-factor x86 boards are extremely expensive and cheaper options are considerably larger in size. These tradeoffs make selection of such a board unfeasible for an aerial drone where space is extremely limited and minimization of cost is a primary concern. As a result, ARM boards (like those in smartphones) are much more attractive - they offer extremely small form-factors, yet remain very affordable. The issue that arises, of course, is that of compatibility - many programs or libraries are not (immediately) available on an ARM installation and require manual compilation of source code using an ARM-based compiler and possible changes to the source code itself first. For this project, an ARM board was selected for the reasons listed above.

@@

The two major choices of sensors for robotic vision are using a laser scanner or an RGB-D camera. Much like the x86 computers, lasers are a terrific choice when cost is not a concern - they have wide field of view (some providing between 270 and 360 degrees), can scan very quickly (40 scans per second), and have amidable range (around 30 meters). However, a single unit can cost upwards of five thousand dollars and using only depth data can result in a large accumulation of error. An RGB-D camera, like the Microsoft Kinect, are very cheap sensors in comparison (the Kinect only costing only \$99 per unit). Unlike the laser, these sensors provide both depth and camera image data and less error is produced as a result of the ability to track image features across frames. However, they are slower (maximum of 30 scans per second) and require sigificantly more bandwidth for data transmission. Due to cost and error concerns, an RGB-D camera was selected for the experiments in this report.

@@

The hardware design of the robot was focused on using low-cost, off-the-shelf components (see Table \ref{tbl: components.}). The approximate cost of a built robot was \$894, significantly cheaper than pre-built alternatives such as the AscTec Pelican used at MIT \cite{bachrach2011range} and University of Washington \cite{bachrach2012estimation} with similar project requirements.

% Table of components used on robot
\begin{table}[h!]
  \centering
  \caption{Table of Components}
  \vspace{2mm}
  \begin{tabular}{l l l}
    \hline \hline
    \vspace{-2mm}
    Component & \multicolumn{1}{l}{Description} & \multicolumn{1}{l}{Cost} \\ [1ex]
    \hline
    & \\
    DJI F450 Frame & Chassis & \$200 \\
    DJI 1045 Propellers & Props & \$10 \\
    DJI 2212 Motors & Actuators & \$30 \\
    12V and 5V Regulators & Power Reg. & \$40 \\
    Zippy 2450 mAh LiPo & Battery & \$30 \\
    64GB ODROID XU3 & ARM SBU & \$240 \\
    Pixhawk PX4 & Controller & \$220 \\
    Microsoft Kinect & Visual Sensor & \$99 \\
    MaxSonar EZ0	& Sonar Sensor & \$25 \\
  \end{tabular}
  \label{tbl: components.}
\end{table}

The robot used a stock F450 frame from DJI, which was not modified in any way - all components were mounted on existing areas using screws or adhesive products.The onboard computational unit chosen was the ODROID XU3 by HardKernel, which has a 1.7Ghz quad-core Snapdragon CPU, 2GB DDR3 RAM, 64GB eMMC flash storage, USB 3.0, and draws 5A. Initially, the robot was equipped with a PandaBoard ES, possessing a 1.2Ghz dual core with 1GB DDR3 RAM, SD card storage, and drawing 3A. Due to low memory and high read/write latencies, the latter board struggled to bear the load of even a full Ubuntu installation and was replaced with the XU3. For the visual sensor, a stripped down Microsoft Kinect Model 1473 was mounted onto the quadcopter - removing the sensor housing reduced weight from a heavy 3 lb to a very nimble 100 g. A Pixhawk PX4 flight controller was also added to the system for actuation control - this allowed the focus of the project to remain on the mapping and flight components of the robot. To accomodate the 12V, 1A requirements of the Kinect and 5V, 5A of the ODROID, several power regulators were mounted and installed to the robot's power system. The entire system was powered by a single 2450 mAh LiPo battery.

@@

@@

\subsection{Overview}

There were a number of key components needed to develop a software architecture for the robot. ROS Hydro was selected as a software package to manage the communication, networking, and overall data representation used throughout the robot, RGBDSLAM\_V2 as an algorithm integrated with ROS to develop the 3-D map onboard the robot, and lastly, MAVROS was an additional ROS package that was used to communicate with the motor controller. The data flow between all the software components can be seen in the Appendix in Figure \ref{fig: data flow.}.

\subsection{RGBDSLAM\_V2}
\noindent In order to compute a 3D map, the quadcopter's onboard computer uses a type of algorithm called SLAM (simultaneous localization and mapping), which computes a map and keeps track of the robotic agent's pose relative to said map. Due to time constraints, it was decided that a proprietary SLAM algorithm was not an option and a previously developed software package was chosen instead. Due to its compatibility with ROS and extensive usage throughout the robotics community, RGBDSLAM\_V2 \cite{endres2012evaluation} was the software used to produce the map and pose transformations of the robot during flight.

% RGBDSLAM data flow
\begin{figure}[h!]
 \caption{Data flow of RGBDSLAM\_V2 \cite{endres2012evaluation}}
 \centering
   \includegraphics[width=0.6\textwidth]{images/rgbdslam}
 \label{fig: rgbdslam.}
\end{figure}

As opposed to sensors like a scanning laser, RGBDSLAM\_V2 provides a SLAM algorithm that can be interfaced with RGB-D sensors like the Microsoft Kinect used throughout this report. The backend of the algorithm consists of a pose graph, as seen in Figure \ref{fig: rgbdslam.}, where each node represents the 3-D pose of the sensor / robot and each edge corresponds to pairwise transformations between sensor poses in the pose graph. This graph is used in tandem with the depth and image data to produce the transformed point clouds in the output map.

@@

Robot Operating System (ROS) is a meta operating system that is installed as package on a UNIX-based OS like Ubuntu or OS X. In a nutshell, ROS allows one to design their robot using a distributed model, where each ROS \textsl{node} is essentially a process or computational component of the robot. It also provides asynchronous and synchronous communication libraries, networking libraries, and supports multiple programming languages. Using said libraries, nodes can obtain information output from other nodes via a subscription or reply-request model as well as output  data themselves in the same fashion. Usage of ROS in the project allowed focus to remain on algorithm development and abstracts out the software glue that connects all the different algorithms running onboard.

% ROS architecture
\begin{figure}[h!]
 \caption{Photograph of finished quadcopter robot.}
 \centering
   \includegraphics[width=0.3\textwidth]{images/rgbdslam}
\end{figure}

Within the system presented in the report, there were several nodes that partitioned the processes running in real time on the robot. RGBDSLAM produced the map and pose of the robot onboard, which were each broadcast to the server when running cooperative mapping. The Map Fusion node was also running on the server (discussed in a later section) which subscribed to said data and produced the global map for all the robots. MAVROS was used onboard the robot to take command requests from the onboard computer and send them to the Pixhawk controller.

@@

In order for the onboard computer to communicate with the Pixhawk controller, it makes use of a ROS package called MAVROS. This runs as another ROS node in the ROS system which allows the computer to send commands to the Pixhawk from a high-level. This includes commands such as arming and disarming of the motors, take-off and landing commands, checking battery levels, and sending RC values to change the state of the motors (move).

@@

MAVROS to communicates with the computer using a data protocol called MAVLINK - this allows a graphical user interface, such as that recommended by the Pixhawk manufacturer, to be used in tandem with MAVROS and that data that it publishes.

@@

Coupled with the mapping component of the RGBDSLAM package, a custom ROS node was written (integrated with RGBDSLAM) that provided a stream of clouds added to the map to through a new ROS topic, each corresponding to new nodes added within the graph. As shown in Figure \ref{fig: online stream.}, these clouds and their respective transforms\footnote{The transform of the cloud is that between the RGB optical frame of the Kinect camera and the fixed frame of the robot's map.} are computed by RGBDSLAM, sent procedurally over the network, received by a server or other external computer, which then executes the online map builder algorithm for each cloud. The algorithm first matches the new cloud $\bf{P_n}$ with its transform $\bf{T_n}$ by performing a transformation lookup keyed by the timestamp $\bf{t_n}$ of the cloud (located in its header data). Once located, the transformation is applied to the cloud, changing its pose to be relative to the aggregate map $\bf{P_a}$. Once this transformation is applied, the new cloud can be simply appended to the current aggregate cloud in the simple operation $\bf{P_a} += \bf{P_n}$  - this new version of the cloud $\bf{P_a}$ is then saved into a database or filesystem.

@@

    \noindent Within the SCIA process itself, there are several subprocesses. First, the normals $N_{source}$ and $N_{target}$ are found by PCL's normal estimator. These normal clouds represent the estimated surface normals at each point in the cloud. They are then used in PCL's Fast Point Feature Histogram (FPFH) \cite{rusu2009fast,rusu2009fastlabel} estimator, to generate approximate feature clouds $F_{source}$ and $F_{target}$. These feature clouds store feature descriptors for each point in the cloud, in this case, FPFH features. Although, the theory behind image features is beyond the scope of this report, the FPFH feature approximates the mean curvature of a point's k-neighbors' geometry with a histogram of values - this type of feature allows computation of a feature cloud in asympototically linear time, giving a powerful but relatively quick feature estimator. Lastly, these feature clouds from this process are used to estimate an initial transformation $T$, which is applied to the initial source cloud to obtain an initial alignment. This gives the clouds a reasonably close placement relative to each other, and allowing optimal usage of second stage of alignment, ICP, to correct their positioning on a finer scale. The parameters used to tune the SCIA process can be seen in Table \ref{tbl: map fusion param.} within the Appendix.

@@

    \noindent After the clouds have passed through the initial alignment stage, they are locally optimized using the Iterative Closest Point algorithm. ICP takes a point cloud $P_{source}$ and finds the nearest k-neighbor points in $P_{target}$. By minimizing the sum of squares error, a rigid transformation $T$ between $P_{source}$ and $P_{target}$ is output. As shown in Figure ~\ref{fig:SCIA alignment.}, this transformation is applied to $P_{source}$ which eliminates narrower errors between the two clouds. The parameters used to tune the ICP process can be seen in Table \ref{tbl: map fusion param.} within the Appendix.

@@

    Lastly, the target and transformed source cloud are concatenated using Point Cloud Library's concatentation features - programmatically, this is as simple as just adding the clouds together. Using another Voxel filter, the excess data points are trimmed away to generate the final stitched version of the map, as shown in Figure ~\ref{fig:ICP alignment.}. The parameters used to tune the filtering process can be seen in Table \ref{tbl: map fusion param.} within the Appendix. \\

@@

% Component data flow diagram
\begin{figure}[h!]
 \caption{Data flow of quadcopter components.}
 \centering
   \includegraphics[width=0.8\textwidth]{images/data_flow}
 \label{fig: data flow.}
\end{figure}

@@

% Table of Map Fusion parameters
\begin{table}[h!]
  \centering
  \caption{Map Fusion Parameters}
  \vspace{2mm}
  \begin{tabular}{l l}
    \hline \hline
    \vspace{-2mm}
    Parameter & \multicolumn{1}{l}{Value} \\ [1ex]
    \hline
    & \\
    Voxel Leaf Size & 0.05 \\
    ICP Max. Corresp. Dist. & 0.1 \\
    ICP Max. Iter. & 50 \\
    ICP Trans. Epsilon & 1e-8 \\
    ICP Euclid. Epsilon & 1 \\
    SCIA Min. Sample. Dist & 1 \\
    SCIA Max. Corresp. Dist & 1 \\
    SCIA Max. Iter. & 50 \\
  \end{tabular}
  \label{tbl: map fusion param.}
\end{table}
